\sysfull

### 2018-04-17 paper/partialcommit.tex

\sys uses {\em task downscaling} to make progress through a task that is too
large to complete using the energy that the device can buffer.  Task
downscaling executes part of the long task and interrupts its execution with a
{\em partial commit}, after which the long task continues.  If power fails, the
partial commit preserves the progress through the task, and execution resumes
from the point of the partial commit, rather than from the start of the task.
Eventually, after some number of partial commits and power failures, the task
will complete and execution will move on to a task with an energy demand
accommodated by the device's energy buffer. Task downscaling violates task
atomicity in a non-terminating execution, favoring continued progress over
atomicity.  If a program requires a task's atomicity over its progress, 
the programmer can disable task downscaling for that task.

>>>>

\sys uses {\em task downscaling} to make progress through a task that is too
large to complete using the energy that the device can buffer.  Task
downscaling executes part of the long task and interrupts its execution with a
{\em partial commit}, after which the long task continues. If power fails, the
partial commit preserves the progress through the task, and execution resumes
from the point of the partial commit, rather than from the start of the task.
Eventually, after some number of partial commits and power failures, the task
will complete and execution will proceed to a task with an energy demand
accommodated by the device's energy buffer. Task downscaling violates task
atomicity in a non-terminating execution, favoring continued progress over
atomicity. If a program requires a task's atomicity over its progress, 
the programmer can disable task downscaling for that task.

### 2018-04-17 paper/systemdescription.tex
move fig 3 up the page

@@

\begin{wrapfigure}{t!}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/graffle/overview.pdf}
	\caption{\sys top-level view. \sys is composed of two core components: \emph{Task Scheduler} and \emph{Memory Manager}.\todo{Redraw figure to map new terms}{Carlo}}
	\label{fig:system_overview}
\end{wrapfigure}

@@

\sys's scheduler {\em downscales} a task to preserve forward progress when a
single task repeatedly fails to execute to completion.  For a repeatedly-failing
task, the scheduler uses a timer that fires at a decreasing interval to
determine where to execute a {\em partial commit} of the task. Partial
commit saves progress through a task that runs for too long to complete
using the device's buffered energy. Eventually, after a series of partial
commits, the too-long task completes --- partial commit favors progress over task atomicity.  
When a task repeatedly fails, the scheduler uses a timer that counts an operating interval
that decreases in length with each failure and \sys partially commits at the end of the interval. 
Section~\ref{sec:task_coalescing} provides details of \sys's task scheduler.
%and relies on the virtual memory manager to gain a full \emph{flexibility} on
%where to split a task. These features distinguish \sys task splitting technique
%from the traditional checkpointing. A checkpointing system that uses voltage
%threshold to place a checkpoint might cause a program to crash if the
%checkpoint happened to be placed between a peripheral initialization and its
%call. If a programmer disables interrupts between the peripheral initialization
%and the call, the program may fail indefinitely to progress since the
%checkpoint may only be deferred. The \sys task downscaling manager, on the
%other hand, triggers a \emph{partial commit} faster than the previous one on a
%repeated failure to guarantee forward progress. Details of task downscaling
%will be given in Section~\ref{sec:task_downsizing}.

\textbf{\sys Virtual Memory Manager.} \sys is able to efficiently coalesce
tasks because of its efficient virtual memory manager. \sys's memory manager
paginates memory and ensures that data in a page remain consistent despite
power interruptions. \sys allows a task to manipulate data in a volatile copy
of a page only. Pages swap between volatile and non-volatile memory, depending
on the capacity of the volatile memory and the program's access pattern. \sys
tracks a task's memory accesses efficiently at page granularity (rather than
using, e.g., costly word-granular tracking). When a task ends, each page it
accessed commits from volatile memory (or from a non-volatile swap region for
dirty pages) back to the non-volatile main memory. Pages efficiently,
atomically commit using a two-phase commit procedure accelerated using hardware
support for direct memory access (DMA). Section~\ref{sec:memory_virtualization}
provides details of \sys's memory manager.

>>>>

\begin{wrapfigure}{t!}{0.45\textwidth}
	\centering
	\includegraphics[width=0.45\columnwidth]{figures/graffle/overview.pdf}
	\caption{\sys top-level view. \sys is composed of two core components: \emph{Task Scheduler} and \emph{Memory Manager}.}
	\label{fig:system_overview}
\end{wrapfigure}

@@

@@

\sys's scheduler {\em downscales} a task to preserve forward progress when a
single task repeatedly fails to execute to completion.  For a repeatedly-failing
task, the scheduler uses a timer that fires at a decreasing interval to
determine where to execute a {\em partial commit} of the task. Partial
commit saves progress through a task that runs for too long to complete
using the device's buffered energy. Eventually, after a series of partial
commits, the too-long task completes---partial commit favors progress over task atomicity.  
When a task repeatedly fails, the scheduler uses a timer that counts an operating interval
that decreases in length with each failure and \sys partially commits at the end of the interval. 
Section~\ref{sec:task_coalescing} provides details of \sys's task scheduler.
%and relies on the virtual memory manager to gain a full \emph{flexibility} on
%where to split a task. These features distinguish \sys task splitting technique
%from the traditional checkpointing. A checkpointing system that uses voltage
%threshold to place a checkpoint might cause a program to crash if the
%checkpoint happened to be placed between a peripheral initialization and its
%call. If a programmer disables interrupts between the peripheral initialization
%and the call, the program may fail indefinitely to progress since the
%checkpoint may only be deferred. The \sys task downscaling manager, on the
%other hand, triggers a \emph{partial commit} faster than the previous one on a
%repeated failure to guarantee forward progress. Details of task downscaling
%will be given in Section~\ref{sec:task_downsizing}.

\textbf{\sys Virtual Memory Manager.} \sys is able to efficiently coalesce
tasks because of its efficient virtual memory manager. \sys's memory manager
paginates memory and ensures that data in a page remain consistent despite
power interruptions. \sys allows a task to manipulate data in a volatile copy
of a page only. Pages swap between volatile and non-volatile memory, depending
on the capacity of the volatile memory and the program's access pattern. \sys
tracks a task's memory accesses efficiently at page granularity (rather than
using, e.g., costly word-granular tracking). When a task ends, each page it
accessed commits from volatile memory (or from a non-volatile swap region for
dirty pages) back to the non-volatile main memory. Pages efficiently,
atomically commit using a two-phase commit procedure accelerated using hardware
support for direct memory access (DMA). Section~\ref{sec:memory_virtulaization}
provides details of \sys's memory manager.
